### 2019-01-16 Sections/about_the_authors.tex
doing a second save
Zuen su bio

\dropcap{Z}{ixin Huang} completed her PhD in physics at the University of Sydney, Australia. She is currently a postdoctoral fellow at the University of Sheffield, UK.

@@

\dropcap{Z}{u-En Su} is a PhD candidate at the University of Science \& Technology China.

>>>>

\dropcap{Z}{ixin Huang} completed her PhD in physics at the University of Sydney, Australia. She is currently a postdoctoral researcher at the University of Sheffield, UK. She has worked on a wide range of topics ranging from quantum metrology and cryptography to experimental quantum optics.

% \comment{Complete this section}

@@

\dropcap{Z}{u-En Su} is a Postdoctoral Fellow at the Technion -- Israel Institute of Technology. He obtained his PhD at the University of Science \& Technology China. His research interests currently include the physical implementation of quantum computation and quantum metrology, primarily based on linear optics and solid-state quantum photonics systems.
